PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

```{r neurological frequencies nmss}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("nmss"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies nmss.ability_taste_food_smell}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmss.ability_taste_food_smell)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmss.ability_taste_food_smell) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmss.severe_taste_smell_loss}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmss.severe_taste_smell_loss)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmss.severe_taste_smell_loss) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("nmsw"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies nmsw.drink_problems_choking_difficulty}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.drink_problems_choking_difficulty)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.drink_problems_choking_difficulty) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.regularly_night_pass_urine}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.regularly_night_pass_urine)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.regularly_night_pass_urine) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.sex_difficult_finding}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.sex_difficult_finding)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.sex_difficult_finding) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.weak_standing_feeling_light}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.weak_standing_feeling_light)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.weak_standing_feeling_light) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.acting_moving_sleep_talking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.acting_moving_sleep_talking)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.acting_moving_sleep_talking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.double_vision}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(nmsw.double_vision)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, nmsw.double_vision) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("tinnitus"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies tinnitus.ears_noises_minutes_head}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(tinnitus.ears_noises_minutes_head)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, tinnitus.ears_noises_minutes_head) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus.ears_noises_minutes_head_frequency}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(tinnitus.ears_noises_minutes_head_frequency)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, tinnitus.ears_noises_minutes_head_frequency) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus.noises_worry_worst_upset}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(tinnitus.noises_worry_worst_upset)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, tinnitus.noises_worry_worst_upset) %>%
  mutate(Prop = round(n/sum(n), 2))
```

**ADD SCORING FOR NEURO MEASURES**
# ALSfrs
```{ALSfrs col names r}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

```

```{ALSfrs row sums r}
dat.raw <- dat.raw %>%
  mutate(als.sum.score =
  rowSums(select(.,als.col.names), na.rm = F)
   )
```

```{ALSfrs frequencies r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(als.sum.score)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, als.sum.score) %>%
  mutate(Prop = round(n/sum(n), 2))

```
# ESS
```{ESS col names r}
ess.col.names <- dat.raw %>%
  select(
    starts_with("ess") & ends_with("numeric")
  ) %>%
  colnames()

```

```{ESS row sums r}
dat.raw <- dat.raw %>%
  mutate(ess.col.names =
   rowSums(select(.,als.col.names), na.rm = F)
   )
```

```{ESS frequencies r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.col.names)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.col.names) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r nmsw col names}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("nmsw") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names

```

```{r scoring NMSW}
dat.raw <- dat.raw %>% 
  mutate(nmsw.sum_score = 
           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
           )

```

>>>>

```{r neurological frequencies nmss}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("nmss"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies nmss.ability_taste_food_smell}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmss.ability_taste_food_smell)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmss.ability_taste_food_smell) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmss.severe_taste_smell_loss}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmss.severe_taste_smell_loss)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmss.severe_taste_smell_loss) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("nmsw"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies nmsw.drink_problems_choking_difficulty}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.drink_problems_choking_difficulty)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.drink_problems_choking_difficulty) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.regularly_night_pass_urine}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.regularly_night_pass_urine)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.regularly_night_pass_urine) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.sex_difficult_finding}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.sex_difficult_finding)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.sex_difficult_finding) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.weak_standing_feeling_light}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.weak_standing_feeling_light)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.weak_standing_feeling_light) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.acting_moving_sleep_talking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.acting_moving_sleep_talking)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.acting_moving_sleep_talking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies nmsw.double_vision}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(nmsw.double_vision)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, nmsw.double_vision) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("tinnitus"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies tinnitus.ears_noises_minutes_head}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(tinnitus.ears_noises_minutes_head)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, tinnitus.ears_noises_minutes_head) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus.ears_noises_minutes_head_frequency}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(tinnitus.ears_noises_minutes_head_frequency)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, tinnitus.ears_noises_minutes_head_frequency) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies tinnitus.noises_worry_worst_upset}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(tinnitus.noises_worry_worst_upset)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, tinnitus.noises_worry_worst_upset) %>%
  mutate(Prop = round(n/sum(n), 2))
```

**ADD SCORING FOR NEURO MEASURES**
